Parsing Postfix log files

### 2008-12-15 doc/logparser-introduction.tex
Improvements to the glossaries appearance. Minor fixes.

Appendix~XXX provides a glossary of terms used in the thesis.

Appendix~XXX provides a list of acronyms used in the thesis.

>>>>

Appendix~\ref{\glsautoprefix{main}} provides a glossary of terms used in
the thesis.

Appendix~\ref{\glsautoprefix{\acronymtype}} provides a list of acronyms
used in the thesis.

Appendix~\ref{\glsautoprefix{postfix}} gives a brief description of Postfix
daemons.

### 2008-12-15 doc/logparser-other-parsers-review.tex
Some minor changes based on the SGAI paper.
Improvements to the glossaries appearance. Minor fixes.

\newpage{} %XXX

@@

XXX UPDATE THE BLURBS\@.

@@

    \item Only \parsername{} makes it possible to parse new log lines
        without extensive and intrusive modifications to the parser;
        \parsername{}'s architecture is described in \sectionref{why
        separate rules, actions, and framework?}.

@@

XXX EXTEND THIS\@.

Each of the parsers was tested with the \numberOFlogFILES{} test log files
described in \sectionref{parser efficiency}.  The data extracted by
\parsername{} is documented in \sectionref{connections table} and
\sectionref{results table}.

XXX LIST THE DATA NOT EXTRACTED BY EACH PARSER\@.

@@

@@

@@

\begin{table}[htb]
    \caption{Summary of parsers' features}
    \empty{}\label{Summary of parsers' features}
    \begin{tabular}{llllll}
        Parser          & Parsed test   & Data              & Custom            & Documentation  & Source       \\
                        & log files?    & store?            & reports?          & quality?       & code?        \\
        \tableline{}%
        \gls{LMA}       & No            & Yes               & No                & Poor           & Yes          \\ 
        Pflogsumm       & Yes           & No                & Partial \dag{}    & Good           & Yes          \\
        Sawmill         & Yes           & Yes               & Searches          & Very good      & \nialpha{}   \\
        Splunk          & Yes           & Yes               & Searches          & Abundant       & No           \\
                        &               &                   & \& reports        & but poor       &              \\
        Isoqlog         & No            & Yes               & No                & Poor           & Yes          \\
        AWStats         & Partially     & Yes               & Partial \dag{}    & Good           & Yes          \\
        Anteater        & No            & No                & No                & Poor           & Yes          \\
        YAALA           & No            & Yes \ddag{}       & Searches          & Poor           & Yes          \\
        Lire            & Yes           & Yes               & Yes               & Reasonable     & Yes          \\
        Logrep          & No            & Yes               & No                & Poor           & Yes          \\
        \parsername{}   & Yes           & Yes \nibeta{}     & No \nichi{}       & XXX            & Yes          \\
        \tableline{}
    \end{tabular}

>>>>

@@

@@

    \item Only \parsername{} makes it possible to parse new log lines
        without extensive and intrusive modifications to the parser;
        \parsernames{} architecture is described in \sectionref{why
        separate rules, actions, and framework?}.

@@

Each of the reviewed parsers was tested with the \numberOFlogFILES{} test log files
described in \sectionref{parser efficiency}.  The data extracted by
\parsername{} is documented in \sectionref{connections table} and
\sectionref{results table}; that list is repeated here, without the
explanations:  server\_ip, server\_hostname, client\_ip, client\_hostname,
helo, queueid, start, end, warning, smtp\_code, sender, recipient, size,
message\_id, data, timestamp.

@@

XXX LIST THE DATA NOT EXTRACTED BY EACH PARSER FROM HERE ON\@.

@@

XXX UPDATE THE BLURBS FROM HERE ON\@.

@@

\begin{table}[htb]
    \caption{Summary of parsers' features}
    \empty{}\label{Summary of parsers' features}
    \begin{tabular}{llllll}
        \tabletopline{}%
        Parser          & Parsed test   & Data              & Custom            & Documentation  & Source       \\
                        & log files?    & store?            & reports?          & quality?       & code?        \\
        \tablemiddleline{}%
        \gls{LMA}       & No            & Yes               & No                & Poor           & Yes          \\ 
        Pflogsumm       & Yes           & No                & Partial \dag{}    & Good           & Yes          \\
        Sawmill         & Yes           & Yes               & Searches          & Very good      & \nialpha{}   \\
        Splunk          & Yes           & Yes               & Searches          & Abundant       & No           \\
                        &               &                   & \& reports        & but poor       &              \\
        Isoqlog         & No            & Yes               & No                & Poor           & Yes          \\
        AWStats         & Partially     & Yes               & Partial \dag{}    & Good           & Yes          \\
        Anteater        & No            & No                & No                & Poor           & Yes          \\
        YAALA           & No            & Yes \ddag{}       & Searches          & Poor           & Yes          \\
        Lire            & Yes           & Yes               & Yes               & Reasonable     & Yes          \\
        Logrep          & No            & Yes               & No                & Poor           & Yes          \\
        \parsername{}   & Yes           & Yes \nibeta{}     & No \nichi{}       & XXX            & Yes          \\
        \tablebottomline{}%
    \end{tabular}
